\normalsize \headingfont \textbf{Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online} \vspace{-1.5em}

### 2024-04-28 ms/main.tex
Updates from Overleaf

\documentclass[12pt,twoside]{article}
\usepackage{silence}
\WarningsOff*
\renewcommand{\abstractname}{\vspace{-\baselineskip}}
\usepackage[dvipsnames]{xcolor}
\usepackage[
linkcolor=darkgray,
colorlinks=true,
urlcolor=darkgray,
pdfstartview={XYZ null null 1.00},
pdfpagemode=UseNone,
citecolor={darkgray},
pdftitle={Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online}
]{hyperref}
\urlstyle{same}
\usepackage{geometry}
 \geometry{left=1.25in,top=1.7in}
\setlength{\parindent}{.5in}
\renewcommand{\baselinestretch}{1.3}
\setlength{\parskip}{\baselineskip}
\usepackage{xcolor}
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\usepackage[labelfont=bf]{caption}
\captionsetup[figure]{labelfont={bf},name={Figure},labelsep=period}
\usepackage{natbib}
\bibliographystyle{apalike}
\usepackage{graphicx}
\graphicspath{{../}}
\usepackage{float}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{placeins}
\usepackage{subcaption}
\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{adjustbox}
\usepackage{dcolumn}
\usepackage{moresize}
\usepackage[nameinlink, capitalize, noabbrev]{cleveref}
\settowidth{\thanksmarkwidth}{*}
\setlength{\thanksmargin}{-\thanksmarkwidth}
\usepackage{titlesec}
\setlength{\droptitle}{-5em}
\setlength\thanksmarkwidth{.5em}
\setlength\thanksmargin{-\thanksmarkwidth}
\titleformat{\section}{\normalfont\bfseries\filcenter}{}{0pt}{}
\titleformat{\subsection}{\normalfont\bfseries\filcenter}{}{0pt}{\itshape}
\titleformat{\subsubsection}{\normalfont\bfseries\filcenter}{}{0pt}{\itshape}
\titlespacing*{\section}
  {0pt}{-.1\baselineskip}{-.1\baselineskip}  
\titlespacing*{\subsection}
   {0pt}{-.1\baselineskip}{-.1\baselineskip}

\usepackage[T1]{fontenc}
\usepackage{fontspec}
\fontspec{Times New Roman}
\date{}
\providecommand{\keywords}[1]
{
   \small	
  \textit{\hspace{-1em} Keywords: } #1
}
\newfontfamily\headingfont[]{Arial}
%Add Author names to headers and footers here:
\fancypagestyle{firstpage}{
  \fancyhf{}% clear all fields
  \fancyfoot[L]{\color{gray} \footnotesize Copyright \copyright 2024 Lucas Shen and Gaurav Sood. Licensed under the Creative Commons Attribution Non-commercial No Derivatives (by-nc-nd). Available at: \url{http://journalqd.org}}%
  \lhead{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2021), 1–n}
\rhead{\color{gray} \footnotesize 10.51685/jqd.2024.011}
}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LO]{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024)}
\fancyhead[RO]{\color{gray} \footnotesize Consumption of Pornography Online \thepage}
\fancyhead[LE]{\color{gray} \footnotesize Lucas Shen and Gaurav Sood}
\fancyhead[RE]{ \color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024) \thepage}
% DO NOT MAKE CHANGES ABOVE THIS LINE
%Article Title goes here
\title{\normalsize \headingfont \textbf{Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online} \vspace{-1.5em}} 
%Author names and affiliations go here, any Acknowledgements / authors' note / disclosure statement goes into \thanks{}
\author{\normalsize Lucas Shen\\ \normalsize National University of Singapore, Singapore
\vspace{1em} \\ \normalsize Gaurav Sood \\ \normalsize Independent Researcher, USA \thanks{Lucas Shen: \href{mailto:lucas@lucasshen.com}{lucas@lucasshen.com}}\thanks{Gaurav Sood: \href{mailto:gsood07@gmail.com}{gsood07@gmail.com}}\thanks{Date submitted: 2023-03-13}} 
\usepackage{lipsum}
\renewcommand\footnotemark{}
\begin{document}
\maketitle
\thispagestyle{firstpage}
\vspace{-8em}

@@

We also use the data to contribute to the small literature connecting political conservatism to opposition to pornography \citep{Peek1982-ua, Woodrum1992-vk}. Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research, using aggregate data has shown that politically conservative states search for pornography more often and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}. Combining individual-level data on partisanship with directly measured pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa. Superficially, our browsing data suggest Republicans in the right tail of the distribution consume more online pornography than Democrats. Adjusting for background attributes like age, gender, etc., however, makes the partisan differences go away. Our findings relate to \cite{Perry2018-cn}, who find that higher levels of religiosity, also linked to political conservatism, are associated with views of pornography as morally wrong while still having viewed pornography. This unexpected finding suggests a discordance between survey responses and reported actions. Republicans may be consuming just as much pornography as Democrats; they are simply saying otherwise.

@@

\subsection{Demographics And Partisan Identification}
\label{subsec:demographics}
YouGov panel file contains data on demographic characteristics like birth year, state of residence, gender, race, and education level. It also contains data on partisan self-identification. Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents. Of the 1,080 people, 82\% leaned either Republican or Democrat. The remaining 18 percent identified as independent. (See Panel B of \cref{tab:characteristics_split_by_party} for a summary of socio-demographic data by party.)

@@

To code pornographic content, we start by assuming all content marked ``Adult'' as pornographic. This includes ``Adult, Business'' (e.g., onlyfans.com) and ``Adult, Entertainment'' (e.g., hentainfox.com). YouGov classifies some domains that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org, as Adult. Given the skew in the data (see \cref{fig:top25_adult} and \cref{fig:top25_nonadult}), we manually checked the top few hundred adult domains (constituting well over 99\% of the adult content consumed) to remove such sites. We code a domain as carrying pornographic content if there is nudity on the landing page or if the site is some form of erotica. Domains without a YouGov category are assumed to be missing completely at random.

@@

In line with previous research \citep{hindman2009myth, Dewan2004-tt}, we find a considerable skew in online media consumption (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult} in \hyperref[sm:smA]{Appendix A}). As \cref{fig:top25_nonadult} shows, the big tech and social media companies occupy most of the top 25 most frequently visited websites. The top 5 non-pornographic sites were visited more than 200,000 times by our panelists. In comparison, the 99th percentile non-pornographic site was visited only 1,652 times by our panelists during the observation period.

There is a similar concentration of visits in adult content, with a few adult sites attracting a bulk of the total traffic. \cref{fig:top25_adult} reports the top 25 pornography sites. The top three pornography sites (``\textit{xvideos.com}'', ``\textit{pornhub.com}'', and ``\textit{xnxx.com}'') are visited more than 6,500 times by the people in our sample during the one-month period. The most visited site, xvideos.com, clocked 311 hours in total from our participants who visited a pornographic site. (Given 361 consumers of online pornography, this translates into an average of 52 minutes of consumption of \textit{xvideos.com} per participant.) Newer platforms such as ``\textit{onlyfans.com}'' are among the most visited pornography sites. Nine sites are above the 99th percentile in pornography visits (2,224 visits). The average time spent on the ten most frequented pornography sites is 12x the average time on all other pornography sites (approximately 109 minutes vs. 9 minutes, \cref{fig:concentration_porn_consumption}). Our finding is consistent with other analyses of traffic to pornographic sites \cite{webporn}.
The average time spent on the ten most frequented pornography sites is 12 times the average time spent on all other pornographic sites (approximately 109 minutes vs. 9 minutes, \cref{fig:concentration_porn_consumption}). This finding is consistent with other analyses of traffic to pornographic sites \citep{webporn}.

@@

\begin{figure}[!ht]
\caption{Hours Spent on Online Pornography and All Other Online Content}
\label{fig:distribution_duration_on_adultsites_fullsample}
     \centering
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/distribution_duration_on_adultsites_fullsample.pdf}
         \caption{Online pornography}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/distribution_duration_on_nonadultsites_fullsample.pdf}
         \caption{Other online content}
     \end{subfigure}
\caption*{\footnotesize \emph{Notes:} 
    Each panel shows the total number of hours for the sample period.
    Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
    The height of the bars indicates the mean of each bin. 
    Capped vertical bars are bootstrapped 95\% confidence intervals (n = 10,000).
    %textbf{FIG??} shows the same figures but only for consumers of pornography.
}
\end{figure}

@@

To help contextualize the above figures, we present statistics on time spent consuming content from the top ten non-adult categories in \cref{tab:top10cat_description}. The median pornography consumer spends more hours on adult content than sites from six non-adult categories. Only three categories, ``Chat and Instant Messaging'' (e.g., google.com, yahoo.com, live.com), ``Business, Social Networking'' (e.g., facebook.com, soocial.com)),  and ``Entertainment, Streaming Media'' (e.g., youtube.com, hulu.com, netflix.com), have higher levels of consumption at the 95th percentile than online pornography.

@@

\begin{figure}[!ht]
\caption{Time Spent on Online Pornography vs. Non-adult Leisure}
\label{fig:tu_prop_entertainment-prop_adult_duration}
     \centering
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_adult.pdf}
         \caption{Entertainment}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_adult.pdf}
         \caption{Shopping}
     \end{subfigure}
\caption*{\footnotesize \emph{Notes:} Lowess between time spent on online pornography and time spent on other non-adult leisure (``entertainment'' and ``shopping''). Observations above the 90th percentile for adult content consumption are omitted to prevent the graph from being dominated by these outliers. (Given we plot a lowess, such truncation doesn't change the relationship we show.) Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com. Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---the top five such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org. Each estimation in the Lowess uses .3 of the sample data.
The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000). Swapping the horizontal axis for adult content excluding adult-related entertainment and shopping sites looks similar (see \cref{fig:tu_prop_entertainment-prop_pure_adult} in \hyperref[sm:smC]{Appendix C}). 
}
\end{figure}

\subsection{Partisan Differences}
\label{subsec:partisan_differences}
As \cref{tab:characteristics_split_by_party} shows, 31.5\% of Democrats consumed at least some pornography over the month vs. 29.4\% of Republicans. The 2\% difference is not statistically significant. Of the partisans who consumed any pornographic content online, \cref{tab:distribution_duration_party} presents the distribution of time spent on pornographic sites by partisan leanings. Republicans spent more time consuming online pornography than Democrats. The median Republican consumer of pornography consumed 1.4 hours of pornography, while the median Democratic consumer of pornography consumed 0.5 hours. A two-sample Kolmogorov-Smirnov test for differences in distribution rejects the null hypothesis (p = .005) (\cref{tab:distribution_duration_party}). In \cref{tab:distribution_prop_duration_party}, we observe similar patterns for time spent on pornography sites as for percentage of total time spent on the web. The median Republican consumer of pornography consumes 4 percent of their online time on pornography, while the median Democratic consumer of pornography consumes 1.3 percent.

%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
        \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
            %\cref{tab:quantile-estimates-time} tabulates the estimates.
            \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

Looking at differences in the percentage of partisans who consume any pornographic content, we find little difference. Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).

@@

Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}). For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}). Add to it that consumers of pornography online tend to be younger (see Panel B of \cref{tab:characteristics_split_by_porn_consumers}). How do differences in age and other such demographic differences between the parties ``explain'' the results? To find out, we control for the following immutable characteristics that predict pornography consumption: age \citep{Wright2013-an, Woodrum1992-vk}, ethnicity \citep{Wright2013-an}, gender \citep{Woodrum1992-vk}, and education level \citep{Woodrum1992-vk}. As \cref{fig:quantile_regression_duration_covariates} and \cref{fig:quantile_regression_prop_duration_covariates} show, once we adjust for confounders, the partisan differences melt away. (For the corresponding table with the various percentiles, see \cref{tab:quantile-estimates-time}.)

%=====================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (with covariates) 
%=====================================================
\begin{figure}[!ht]
	\centering
	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates)}
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
  \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
	}
	\label{fig:quantile_regression_duration_covariates}
\end{figure}

>>>>

\documentclass[12pt,twoside]{article}
\usepackage{silence}
\WarningsOff*
\renewcommand{\abstractname}{\vspace{-\baselineskip}}
\usepackage[dvipsnames]{xcolor}
\usepackage[
linkcolor=darkgray,
colorlinks=true,
urlcolor=darkgray,
pdfstartview={XYZ null null 1.00},
pdfpagemode=UseNone,
citecolor={darkgray},
pdftitle={Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online}
]{hyperref}
\urlstyle{same}
\usepackage{geometry}
 \geometry{left=1.25in,top=1.7in}
\setlength{\parindent}{.5in}
\renewcommand{\baselinestretch}{1.3}
\setlength{\parskip}{\baselineskip}
\usepackage{xcolor}
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\usepackage[labelfont=bf]{caption}
\captionsetup[figure]{labelfont={bf},name={Figure},labelsep=period}
\usepackage{natbib}
\bibliographystyle{apalike}
\usepackage{graphicx}
\setlength{\abovecaptionskip}{0pt}
\graphicspath{{../}}
\usepackage{float}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{placeins}
\usepackage{subcaption}
\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{adjustbox}
\usepackage{dcolumn}
\usepackage{moresize}
\usepackage[nameinlink, capitalize, noabbrev]{cleveref}
\settowidth{\thanksmarkwidth}{*}
\setlength{\thanksmargin}{-\thanksmarkwidth}
\usepackage{titlesec}
\setlength{\droptitle}{-5em}
\setlength\thanksmarkwidth{.5em}
\setlength\thanksmargin{-\thanksmarkwidth}
\titleformat{\section}{\normalfont\bfseries\filcenter}{}{0pt}{}
\titleformat{\subsection}{\normalfont\bfseries\filcenter}{}{0pt}{\itshape}
\titleformat{\subsubsection}{\normalfont\bfseries\filcenter}{}{0pt}{\itshape}
\titlespacing*{\section}
  {0pt}{-.1\baselineskip}{-.1\baselineskip}  
\titlespacing*{\subsection}
   {0pt}{-.1\baselineskip}{-.1\baselineskip}

\usepackage[T1]{fontenc}
\usepackage{fontspec}
\fontspec{Times New Roman}
\date{}
\providecommand{\keywords}[1]
{
   \small	
  \textit{\hspace{-1em} Keywords: } #1
}
\newfontfamily\headingfont[]{Arial}
%Add Author names to headers and footers here:
\fancypagestyle{firstpage}{
  \fancyhf{}% clear all fields
  \fancyfoot[L]{\color{gray} \footnotesize Copyright \copyright 2024 Lucas Shen and Gaurav Sood. Licensed under the Creative Commons Attribution Non-commercial No Derivatives (by-nc-nd). Available at: \url{http://journalqd.org}}%
  \lhead{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024), 1–n}
\rhead{\color{gray} \footnotesize 10.51685/jqd.2024.011}
}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LO]{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024)}
\fancyhead[RO]{\color{gray} \footnotesize Consumption of Pornography Online \thepage}
\fancyhead[LE]{\color{gray} \footnotesize Lucas Shen and Gaurav Sood}
\fancyhead[RE]{ \color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024) \thepage}
% DO NOT MAKE CHANGES ABOVE THIS LINE
%Article Title goes here
\title{\normalsize \headingfont \textbf{Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online} \vspace{-1.5em}} 
%Author names and affiliations go here, any Acknowledgements / authors' note / disclosure statement goes into \thanks{}
\author{\normalsize Lucas Shen\\ \normalsize National University of Singapore, Singapore
\vspace{1em} \\ \normalsize Gaurav Sood \\ \normalsize Independent Researcher, USA \thanks{Lucas Shen: \href{mailto:lucas@lucasshen.com}{lucas@lucasshen.com}}\thanks{Gaurav Sood: \href{mailto:gsood07@gmail.com}{gsood07@gmail.com}}\thanks{Date submitted: 2023-03-13}} 
\usepackage{lipsum}
\renewcommand\footnotemark{}
\begin{document}
\maketitle
\thispagestyle{firstpage}
\vspace{-8em}

@@

We also use the data to contribute to the small literature connecting political conservatism to opposition to pornography \citep{Peek1982-ua, Woodrum1992-vk}. Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research using aggregate data has shown that politically conservative states search for pornography more often and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}. Combining individual-level data on partisanship with directly measured pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa. Superficially, our browsing data suggest Republicans in the right tail of the distribution consume more online pornography than Democrats. Adjusting for background attributes (e.g., age, gender, race, education), however, makes the partisan differences go away. Our findings relate to \cite{Perry2018-cn}, who find that higher levels of religiosity, also linked to political conservatism, are associated with views of pornography as morally wrong while still having viewed pornography. This unexpected finding suggests a discordance between survey responses and reported actions. Republicans may be consuming just as much pornography as Democrats; they are simply saying otherwise.

@@

\subsection{Demographics And Partisan Identification}
\label{subsec:demographics}
YouGov panel file contains data on demographic characteristics like birth year, state of residence, gender, race, and education level. It also contains data on partisan self-identification. Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents. Of the 1,080 people, 82\% leaned either Republican or Democrat. The remaining 18 percent identified as independent. (See Panel B of \cref{tab:characteristics_split_by_party} and \cref{tab:characteristics_split_by_porn_consumers} for a summary of socio-demographic data by party.)

@@

To code pornographic content, we start by assuming all content marked ``Adult'' as pornographic. This includes ``Adult, Business'' (e.g., onlyfans.com) and ``Adult, Entertainment'' (e.g., hentainfox.com). YouGov classifies some domains that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org, as Adult. Given the skew in the data (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult}), we manually checked the top few hundred adult domains (constituting well over 99\% of the adult content consumed) to remove such sites. We code a domain as carrying pornographic content if there is nudity on the landing page or if the site is some form of erotica. Domains without a YouGov category are assumed to be non-pornographic sites.\footnote{
    We replicate key findings by dropping observations on all sites without YouGov category instead of assuming that only non-pornographic sites have absent YouGov categories. 
    This difference in assumption only affects results on proportion-based measures of consumption through the baseline on total duration. 
    We find a similar skew in pornographic consumption. 
    We also find that partisan differences disappear once we adjust for the baseline characteristics. 
    \hyperref[sm:smH]{Appendix H} reports these results.
}

@@

In line with previous research \citep{hindman2009myth, Dewan2004-tt}, we find a considerable skew in online media consumption (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult} in \hyperref[sm:smA]{Appendix A}). As \cref{fig:top25_nonadult} shows, the big tech and social media companies occupy most of the top 25 most frequently visited websites. Each of the top 5 non-pornographic sites were visited more than 200,000 times by our panelists. In comparison, the 99th percentile non-pornographic site was visited only 1,652 times by our panelists during the observation period.

There is a similar concentration of visits in adult content, with a few adult sites attracting a bulk of the total traffic. \cref{fig:top25_adult} reports the top 25 pornography sites. The top three pornography sites (``\textit{xvideos.com}'', ``\textit{pornhub.com}'', and ``\textit{xnxx.com}'') are each visited more than 6,500 times by the people in our sample during the one-month period. The most visited site, xvideos.com, clocked 311 hours in total from our participants who visited a pornographic site. (Given 361 consumers of online pornography, this translates into an average of 52 minutes of consumption of \textit{xvideos.com} per participant.) Newer platforms such as ``\textit{onlyfans.com}'' are among the most visited pornography sites. Nine sites are above the 99th percentile in pornography visits (2,224 visits). The average time spent on the ten most frequented pornography sites is 12 times the average time on all other pornography sites (approximately 109 minutes vs. 9 minutes, \cref{fig:concentration_porn_consumption}). Our finding is consistent with other analyses of traffic to pornographic sites \cite{webporn}.

@@

\begin{figure}[!ht]
     \centering
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/distribution_duration_on_adultsites_fullsample.pdf}
         \caption{Online pornography}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/distribution_duration_on_nonadultsites_fullsample.pdf}
         \caption{Other online content}
     \end{subfigure}
\caption{Hours Spent on Online Pornography and All Other Online Content}
\label{fig:distribution_duration_on_adultsites_fullsample}
\caption*{\footnotesize \emph{Notes:} 
    Each panel shows the average hours per decile for the sample period.
    Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
    The height of the bars indicates the mean of each bin. 
    Capped vertical bars are bootstrapped 95\% confidence intervals (n = 10,000).
    %textbf{FIG??} shows the same figures but only for consumers of pornography.
}
\end{figure}

@@

To help contextualize the above figures, we present statistics on time spent consuming content from the top ten non-adult categories in \cref{tab:top10cat_description}. 
The median pornography consumer (\cref{tab:distribution_duration}) spends at least as many hours on adult content as the median online user on sites from six non-adult categories. 
Only three categories, ``Business, Social Networking'' (e.g., facebook.com, soocial.com)), ``Chat and Instant Messaging'' (e.g., google.com, yahoo.com, live.com), and ``Entertainment, Streaming Media'' (e.g., youtube.com, hulu.com, netflix.com), have higher levels of consumption at the 95th percentile than online pornography.

@@

\begin{figure}[!ht]
\label{fig:tu_prop_entertainment-prop_adult_duration}
     \centering
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_adult.pdf}
         \caption{Entertainment}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_adult.pdf}
         \caption{Shopping}
     \end{subfigure}
\caption{Time Spent on Online Pornography vs. Non-adult Leisure}
\caption*{\footnotesize \emph{Notes:} Lowess between time spent on online pornography and time spent on other non-adult leisure (``entertainment'' and ``shopping''). Observations above the 90th percentile for adult content consumption are omitted to prevent the graph from being dominated by these outliers. (Given we plot a lowess, such truncation doesn't change the relationship we show.) Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com. Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---the top five such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org. Each estimation in the Lowess uses .3 of the sample data.
The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000). Swapping the horizontal axis for adult content excluding adult-related entertainment and shopping sites looks similar (see \cref{fig:tu_prop_entertainment-prop_pure_adult} in \hyperref[sm:smC]{Appendix C}). 
}
\end{figure}

\subsection{Partisan Differences}
\label{subsec:partisan_differences}
As \cref{tab:characteristics_split_by_party} shows, 31.5\% of Democrats consumed at least some pornography over the month vs. 29.4\% of Republicans. The 2\% difference is not statistically significant (p = .57). Of the partisans who consumed any pornographic content online, \cref{tab:distribution_duration_party} presents the distribution of time spent on pornographic sites by partisan leanings. Republicans spent more time consuming online pornography than Democrats. The median Republican consumer of pornography consumed 1.4 hours of pornography, while the median Democratic consumer of pornography consumed 0.5 hours. A two-sample Kolmogorov-Smirnov test for differences in distribution rejects the null hypothesis (p = .005) (\cref{tab:distribution_duration_party}). In \cref{tab:distribution_prop_duration_party}, we observe similar patterns for time spent on pornography sites as for percentage of total time spent on the web. The median Republican consumer of pornography consumes 4 percent of their online time on pornography, while the median Democratic consumer of pornography consumes 1.3 percent.\footnote{
    With the missing at-random assumption, the Republican consumer of pornography consumes 4.2 percent of their online time on pornography, while the median Democratic consumer of pornography consumes 1.5 percent (\cref{tab:distribution_prop_duration_party_mar}).
}

%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_duration_adult.pdf}
	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
        \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_proportion_duration_adult.pdf}
	\caption{Quantile Estimates--Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
            %\cref{tab:quantile-estimates-time} tabulates the estimates.
            \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

Looking at differences in the percentage of partisans who consume any pornographic content, we find little difference as well. Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).

@@

%=====================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (with covariates) 
%=====================================================
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
  \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
	}
	\label{fig:quantile_regression_duration_covariates}
\end{figure}

%================================================================
% Fig of quantile regression estimates
% Percentage Time Spent on Adult Sites by Party (with covariates) 
%================================================================
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
	\caption{Quantile Estimates--Partisan Differences in the Percentage of Time Spent on Pornographic Sites (with covariates)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Covariates included: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
        \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
	}
	\label{fig:quantile_regression_prop_duration_covariates}
\end{figure}

Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}). For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}). Add to it that consumers of pornography online tend to be younger (see Panel B of \cref{tab:characteristics_split_by_porn_consumers}). How do differences in age and other such demographic differences between the parties ``explain'' the results? To find out, we control for the following immutable characteristics that predict pornography consumption: age \citep{Wright2013-an, Woodrum1992-vk}, ethnicity \citep{Wright2013-an}, gender \citep{Woodrum1992-vk}, and education level \citep{Woodrum1992-vk}. As \cref{fig:quantile_regression_duration_covariates} and \cref{fig:quantile_regression_prop_duration_covariates} show, once we adjust for confounders, the partisan differences melt away. 
%(For the corresponding table with the various percentiles, see \cref{tab:quantile-estimates-time}.) 
%Using alternative classifications of pornography sites led to similar conclusions (\cref{sec:robustness}).
